---
title: "Fun with Yelp"
output:
  pdf_document: default
  html_notebook: default
---

In this document I am going to inspect a free data resource from Yelp in order to find interesting questions that can be further analysed.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r "setup", include=FALSE, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_knit$set(root.dir = '../')
star_pred_model_xgb <- readRDS('model_xgb.rds')
df.business_agg <- readRDS('df_business_agg.rds')
df.count_business <- readRDS('df_count_business.rds')
require('pacman')
p_load('wordcloud')
p_load('caret')
p_load('kableExtra')
```

```{r wordcloud, results='asis', echo=FALSE,fig.align='center'}
wordcloud(words = df.count_business$word, freq = df.count_business$n, min.freq = 1,
          max.words=150, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```


```{r wordcount, results='asis', echo=FALSE,fig.align='center'}

```

```{r table,results='asis', warning=FALSE, cache=TRUE, message=FALSE,fig.align='center'}
df <- varImp(star_pred_model_xgb)
kable(df$importance)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
