---
title: "Fun with Yelp"
output:
  pdf_document: default
  html_notebook: default
---

In this document I am going to inspect a free data resource from Yelp in order to find interesting questions that can be further analysed.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r "setup", include=FALSE}
knitr::opts_knit$set(root.dir = '../')
source("main.R", chdir = T)
```

```{r}
 glimpse(yelp_user.csv)
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
